Keystoneness, centrality, and the structural controllability of ecological networks

### 2018-07-19 paper/reviewers-response.Rmd

---
title: "Keystoneness, centrality, and the structural controllability of ecological networks"
subtitle: "JEcol-2017-0720 - Detailed response to comments"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \usepackage{lineno}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}
  - \externaldocument[S-]{supp-info}
  - \usepackage[most]{tcolorbox}
  - \definecolor{block-gray}{gray}{0.9}
  - \newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}
---

### 2018-07-19 paper/manuscript.Rmd
Settle on a title

---
title: "Species with high control capacity support stable coexistence of pollination networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

>>>>

---
title: "Keystoneness, centrality, and the structural controllability of ecological networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---
